---
title: "1. mapview basics"
output:
  rmarkdown::html_document:
    toc: yes
    toc_float: yes
    theme: united
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(fig.width = 8.83, message = FALSE)
```

**mapview** is intended to provide a quick and easy way to visualize/plot spatial data in an interactive manner. As such, a one-liner is enough to produce an interactive map view of the data. Methods are defined for all objects from packages **sf**, **sp**, **raster** and **satellite**.

# Vector data

**mapview** includes 3 vector type data sets: 

* `breweries` - a selection of (micro-) breweries in Franconia, Bavaria.
* `trails` - slected hiking trails in Franconia (not used in this vignette).
* `franconia` - administrative regions of Franconia at the district level.


For vector data a call to `mapview` without any further arguments will produce a default map view including:

* a layer control to switch between 5 different background maps
* a scale bar
* information on mouse cursor position and zoom level of the current view
* a zoom-to-layer button to easily navigate to the displayed layer
* popups listing all attribute entries of the respective features (when clicked)
* labels of the feature IDs (when hovered over)
* zoom control buttons provided by the underlying **leaflet** map
* attribution information of the active map layer in the bottom right corener of the map

Here's an example for each vector type:

```{r points}
library(mapview)
mapview(breweries)
```
